p-NLI: a Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models

### 2018-03-22 paper/background.tex
update test
update background

\section{Background}

\begin{itemize}
    \item Motivation for : reading comprehension, similarity of sentennce
    \item what is it?
    \item its connection with other NLP tasks (one of the key)
    \item
\end{itemize}

@@

%

\subsection{Interprebilty Challenges}

Compared with Conputer Vision, the discrete nature of words and sentences 
presents additional challenge for
interpreting the model, since many visualization technique often employed
for images rely on continuous nature of the input space (e.g., one can interpolate
real values much easier than interplolate between words/sentences).

On the other hand, a majority of recent NLP neural networks share the nature of 
end-to-end model, where the entire model operates as a black-box that takes 
vectorized input and yields final prediction for a specific task.
Therefore, to study the inside of end-to-end neural models, it is important to 
explore the interaction between intermediate representations and predictions.

@@

% The introduction of attention mechanism~\cite{} allow simpler models to match or even outperform more complex / deeper models by exploiting the alignment of bits of local text between sentences. The new challenges

@@

>>>>

\section{Background}
\label{sec:languageInference}

In order to full appreciate the technqiue discussed in this paper, certain background
in neural network and more specifically neural natural language process models are necessary.
In the following paragraphs, we aim to cover the most relevent backgound knowledge.

\shusen{high level NLP comments}

@@

\subsection{Neural Network Primer}
\shusen{What is the basic understanding of neural network What is the end-to-end}

\subsection{Neural Network Model in NLP}
% \subsection{Interprebilty Challenges}
Compared with Conputer Vision, the discrete nature of words and sentences
presents additional challenge for
interpreting the model, since many visualization technique often employed
for images rely on continuous nature of the input space (e.g., one can interpolate
real values much easier than interplolate between words/sentences).
%
On the other hand, a majority of recent NLP neural networks share the nature of
end-to-end model, where the entire model operates as a black-box that takes
vectorized input and yields final prediction for a specific task.
Therefore, to study the inside of end-to-end neural models, it is important to
explore the interaction between intermediate representations and predictions.

@@

@@

\shusen{What is the most standard example to illustrate NLI problem?}
